---
output:
  html_document: default
  pdf_document: default
---
Red Wine Quality by Chelsey De Dios
========================================================
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
#importing libraries
library(gridExtra)
library(ggplot2)
library(tidyverse)
library(ggpubr)
```

```{r echo=FALSE, Load_the_Data}
#loading red wine data
wine <- read.csv("wineQualityReds.csv")
```

We will be exploring data regarding qualities of nearly 1600 red wines.
This dataset includes a variety of objective observations on red wine and a 
rating of the wines based on analysis by a group of wine experts. I chose this
dataset as I used to be a server at a high end restaurant and I would be 
interested to know if the conventional knowledge that we were taught to help
customers is true within this dataset.

# Univariate Plots Section

## Statistical Summary

```{r echo=FALSE, Univariate_Plots}
#summary of red wine data
summary(wine)
```
Here in our statistical summary we see we have mostly objective, measurable 
observations about the wine, with just quality being a subjective measure of the 
wines. There are 1599 observations and 13 variables.


## Data Structure

```{r echo=FALSE, message=FALSE, warning=FALSE}
#getting data structure
str(wine)
```
Now looking at our data structure we see we are dealing with some very small 
numbers. Quality is, notably, an integer. This is inconvenient for our purposes
because it will cause the graphs to make singular plots. It would be better if
quality were treated as a numeric, so let's change that.

```{r echo=FALSE, message=FALSE, warning=FALSE}
#changing quality to a numeric value and observing the output
wine$quality <- as.numeric(wine$quality)
str(wine)
```


## Wine Quality

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot wine quality bar graph
qplot(x = wine$quality, 
      xlab = "Quality Rating 1-10", 
      binwidth = 1)+
      scale_x_continuous(breaks = seq(0,10,1))
```

It looks like most of the wine with of middling quality according to our experts
with most having a score of 5-6 out of 10. This makes me wonder about how this
data was collected, and why so few were rated as exceptionally poor or excellent


## Alcohol Content By Volume

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol bar graph
qplot(x = wine$alcohol, 
      xlab = "Alcohol Content (% by volume)", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,15,.5))
```

Here we can see that the bulk of our alcohol content is between 9% and 11% by
volume with a little bit of an outlier around ~14.75%


## Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot residual sugar bar graph
qplot(x = wine$residual.sugar, 
      xlab = "Residual Sugar (g / dm^3)", 
      binwidth = 1)+
      scale_x_continuous(breaks = seq(0,16,1))
```

Our residual sugar is positively skewed with most of the data within 
1.5-3 g / dm^3. There are some pretty far out numbers going up to around 
15.5 g / dm^3. Seeing that most of the residual sugar is in the 1.5-3.5 g/dm^3
is a huge alarm for me. Sugar in wine varies greatly and can be anywhere from
0 to over 200 g/L (g/L is equivalent to g/dm^3) The fact that we only have wines
under 20 g/L tells me we are dealing with only dry wines. There should be a
relationship with sugar and alcohol content, as wines with more alcohol should 
have less sugar as sugar is eaten by yeast to make alcohol in wine.


## Density

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot density bar graph
qplot(x = wine$density, 
      xlab = "density (g / cm^3)", 
      binwidth = .001)+
      scale_x_continuous(breaks = seq(0,2,.001 ))
```

Our density has a nice, normal distribution with most wines falling between .995
and .999 g/cm^3. There should be a relationship between alcohol, sugar
and density, as sugar rich wines should be thicker while alcohol rich wines
should be thinner.


##  Sulphates

```{r echo=FALSE}
#code to plot sulphates bar graph
qplot(x = wine$sulphates, 
      xlab = "potassium sulphate (g / dm3)", 
      binwidth = .05)+
      scale_x_continuous(breaks = seq(0,2,.1 ))
```

Our sulphates seem to have a fairly normal distribution save for a few outliers.
sulphates are used to preserve wine, as our data's accompanying text file 
indicates it is an antimicrobial and an antioxidant which leads to sulfur 
dioxide or sulphites in wine.


##  Total and Free Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot total sulfur dioxide bar graph
qplot(x = wine$total.sulfur.dioxide, 
      xlab = "total sulfur dioxide (mg / dm^3)", 
      binwidth = 10)+
      scale_x_continuous(breaks = seq(0,300,10 ))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to free sulfuree dioxide bar graph
qplot(x = wine$free.sulfur.dioxide, 
      xlab = "free sulfur dioxide (mg / dm^3)", 
      binwidth = 2)+
      scale_x_continuous(breaks = seq(0,72,2 ))
```

The free sulfur dioxide has a positive skew as does our total sulfur dioxide. 
Wine makers may be trying to keep these numbers low as sulphites have an 
undeservedly bad reputation, a topic for another day. 

Later on in our analysis I would be interested to see if our wine experts 
noticed any difference in our sulphate/sulphite rich wine and those that are
less so. I expect that we will find that they didn't spot the difference. We 
should find that there is an relationship between sulphates/sulphites
and alcohol content, as alcohol rich wines should not need as much preservative
as those wines with less alcohol.


## Fixed and Volatile Acidity

```{r echo=FALSE}
#code to plot fixed acidity bar graph
qplot(x = wine$fixed.acidity, 
      xlab = "fixed acidity", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,16,.5))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot volatile acidity bar graph
qplot(x = wine$volatile.acidity, 
      xlab = "Volatile Acidity", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,2,.1))
```

Our volatile acidity also seems to have a fairly normal distribution. It will be
interesting to see the relationship between sugar, chloride, acidity, citric
acid and quality later on.


## Citric Acid

```{r echo=FALSE}
#code to plot citric acid bar graph
qplot(x = wine$citric.acid, 
      xlab = "citric acid", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,1,.05))
```

Here we see that our citric acid is pretty evenly distrbuted between 0 and .5.
It is interesting that the distribution fell this neatly.



# Univariate Analysis

### What is the structure of your dataset?

Our dataset has 1599 observations with 13 variables all numeric since we
converted our integer of quality to numeric to make the data easier to work with

We have a lot of middling quality wines so it makes it more difficult to spot
what it was that necessarily put the higher quality wines at that rating. If our
data had more very low and very high quality wines vs just a bunch of average
wines we might be able to draw more meaningful conclusions than I believe we
will find here today.



### What is/are the main feature(s) of interest in your dataset?

* I am interested in what factors put some wines at a higher quality rating than
others, particularly if sulphates/sulphites made much of a difference to our
experts. 

* I am interested in the relationship of alcohol content to preservatives,
including acids and sulphates/sulphites.

* There should be a relationship between alcohol and sugar content and density. 

* I would like to explore the relationship between volatile acidity and citric
acid as I would expect that there volatile acidity would go up with the addition
of citric acid.

### Of the features you investigated, were there any unusual distributions? \

Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I did change wine quality from an integers to a numeric so that it could be 
graphed on a continuous scale.

As far as unusual distributions, most of our data is either positively skewed or
has a relatively normal distribution, suggesting that less is more for wine
makers when it comes to any of these factors. Maybe they want to let the flavor
of the grapes do the talking instead of making an extreme flavor in any
direction.

The residual sugar of the wines is very low. We are dealing with a subset of
very dry wines, which seems unusual.
----
----

# Bivariate Plots Section

----

## Variables to Quality Comparisons

----

### Sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to sulphates jitter plot
ggplot(aes(x = quality, y = sulphates), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  xlab("quality")
```

It appears that sulphates in wine do not have a negative effect on quality as I
expected, despite some people's misgivings about the nature of sulphates in food
and beverage. In fact, on this plot it appears that the more sulphates were in
the wine the higher the rating the flavor of the wine got.


### Total Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to total sulfur dioxide jitter plot
ggplot(aes(x = quality, y = total.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  xlab("quality")
```

Here we see that the total sulfur dioxide seems to have a weak negative 
relationship with quality. Indeed, our text file suggests that the more total
sulfur dioxide there is, the more prominent their flavor can be, which must
be unfavorable


### Free Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to  free sulfur dioxide jitter plot

ggplot(aes(x = quality, y = free.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  xlab("quality")
```

In the free sulfur dioxide and the total sulfur dioxide to quality graphs we
see a very weak relationship. There is likely no relationship between free 
sulfur dioxide content and perceived quality of wine.


### Fixed Acidity

```{r echo=FALSE}
#code to plot quality to fixed acidity jitter plot

ggplot(aes(x = quality, y = fixed.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

Our fixed acidity appears to have a weak positive relationship with quality.


### Volatile Acidity

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to volatile acidity jitter plot

ggplot(aes(x = quality, y = volatile.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

More volatile acidity seems to decrease quality with a borderline weak/moderate
relationship.


### Citric Acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to citric acid jitter plot

ggplot(aes(x = quality, y = citric.acid), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The quality of wine seems to improve with citric acid with a weak relationship.


### Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to residual sugar jitter plot

ggplot(aes(x = quality, y = residual.sugar), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The residual sugar does not seem to have much of an effect on quality. This is
likely due to the fact that most of the wines have a very similar amount of 
residual sugar.


### Chlorides

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to chlorides jitter plot

ggplot(aes(x = quality, y = chlorides), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

There is a very weak negative correlation with salt/chlorides and quality.


### Density

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to density jitter plot

ggplot(aes(x = quality, y = density), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

A similarly weak relationship exists between density and quality, with a minor
skew toward lower density/more watery wines. Lower density wines should have a
higher alcohol content and so it is hard to tell which of these variables cause
the preference.


### pH

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to pH jitter plot

ggplot(aes(x = quality, y = pH), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

There does not seem to be much of a relationship between quality and pH


### Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to alcohol jitter plot

ggplot(aes(x = quality, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The relationship between alcohol content and quality seems to be stronger than
most of the data that we have looked at so far where the more alcohol the higher
the quality of the wine. Alcohol leads to dryer flavors in wine and this looks
more and more like this tasting was intended to find the best dry wine.


## Residual Sugar to Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot residual sugar to alcohol jitter plot

ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(1,16,1))
```

Now this graph is interesting because it does not seem to point to the expected
conclusion that the amount of residual sugar would be roughly inversely
proportionate to the amount of alcohol in the wine. Between 1.5 and 3 g/dm^3 of
sugar the alcohol content varies from less than 8.5% to over 14% by volume. We
can see in the outlier range there looks like there is a negative relationship
with the alcohol content going down as the residual sugar goes up, but most of
the data does not follow our expected trend. Our R value seems to indicate a
very weak positive correlation between our variables. This is likely due to the
very limited range of sugar in our wines giving us unlikely data.

Let's zoom in on to the bulk of the data area to see if we see any other trends

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot zoom in on residual sugar to alcohol jitter plot

ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(1.5,3,.1))+
  coord_cartesian(xlim = c(1.5,3))+
  geom_smooth(method = "lm", formula = y~x)
```

So our graph does not at all show the relationship we are expecting here. 


## Alcohol to Preservatives

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total sulfur dioxide jitter plot

ggplot(aes(x = alcohol, y = total.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to free sulfur dioxide jitter plot
ggplot(aes(x = alcohol, y = free.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to fixed acidity jitter plot
ggplot(aes(x = alcohol, y = fixed.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total volatile acidity jitter plot
ggplot(aes(x = alcohol, y = volatile.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

Here, as should be expected, we see that the higher the alcohol content, the
lower the preservatives in the wine. The relationship is weak across the board
with volatile acidity and total sulfur dioxide having the strongest inverse
relationships with alcohol.


## Volatile Acidity to Citric Acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot volatile acidity to citric acid scatter plot
ggplot(aes(x = volatile.acidity, y = citric.acid), data = wine)+
  geom_point(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  scale_y_continuous(breaks = seq(0, 1 , .1))+
  coord_cartesian(ylim = c(0,1))
```

There seems to be a moderate negative correlation with citric acid and volatile
acidity. This goes against what I would have thought since citric acid is added
after wine is made I would have expected that the volatile acidity would 
increase with the addition of citric acid.


## Density to Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot density to alcohol jitter plot
ggplot(aes(x = density, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,2,.001 ))+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

In this graph, as we would expect, the density of the wine goes down as the
alcohol content goes up. Oddly, we would expect this because the alcohol is
created by yeast eating sugar, so it's strange with the uniform sugar content
that this relationship is maintained.


## Density to Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total residual sugar jitter plot
ggplot(aes(x = density, y = residual.sugar), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,2,.001 ))+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

Though the relationship is a bit weaker, we can see that the relationship 
between density and sugar is maintained where the with should be more dense the
more sugar it contains.



# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset? Did you observe any interesting relationships between the other \
features (not the main feature(s) of interest)? What was the strongest \
relationship you found?

The biggest predictors of wine quality by itself was mostly alcohol. Alcohol
had a moderate relationship with wine quality with an r value of .48. Second to
that was volatile acidity where it seems that the more volatile acidity there
was the less liked was the wine. As explained in our text file, a lot of 
volatile acide leads to a vinegary taste in wine which many fine abhorrent so
this data point makes sense. Citric acid seemed to be well liked with a 
coefficient of .23. I remember a manager touting that it added a springy, light
taste to the wine that people enjoyed and it seems our experts agree to some 
extent. Our text file indicates something similar that the citric acid adds a
'freshness' to wine. 

There seemed to be no negative relationship with quality and sulphates in the
alcohol, even perhaps, a weak positive correlation, though the more total sulfur 
dioxide there was the worse of a rating the wine got. The free sulfur dioxide
seemed to make little difference in the wine quality.

Our sugar to alcohol relationship should have been inverse, but according to
this data there is a very weak relationship. Despite this, the expected
relationship of sugar to density and alcohol to density is as we expected with
the higher sugar wines being more dense and the higher alcohol wines being less
dense.

The strongest relationship was alcohol to density with a -.5 correlational
coefficient indicating that there is a moderate relationship between those 
variables. 

Our total sulfur dioxide, free sulfur dioxide, fixed acidity and volatile 
acidity to alcohol comparisons showed a weak negative relationship across the
board giving some bit of credence to our hypotheses that the more alcohol a
wine had, the less preservatives a wine make might add to it.




# Multivariate Plots Section

```{r echo=FALSE}
#code to plot fixed acidity to volatile acidity to citric acid jitter plot
ggplot(aes(x = fixed.acidity, y = volatile.acidity, color = citric.acid), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

This graph shows that our while our citric acid decreases with volatile acidity
it increases with fixed acidity. I don't know why I didn't think to look at that
before, it appears that it is just an acid that does not evaporate readily as is
necessary to be included in our volatile acidity. For fun let's check out the
bivariate graph of that relationship

```{r echo=FALSE}
#code to plot fixed acidity to citric acid scatter plot
ggplot(aes(x = fixed.acidity, y = citric.acid), data = wine)+
  geom_point(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  scale_y_continuous(breaks = seq(0, 1 , .1))+
  coord_cartesian(ylim = c(0,1))
```

Indeed there is a strong correlation between citric acid and fixed acidity

```{r echo=FALSE}
#code to plot alcohol to residual sugar to density jitter plot
ggplot(aes(x = alcohol, y = residual.sugar, 
           color = density), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

Here we show again that the lower the alcohol and the higher the residual sugar
the higher the density, and the higher the alcohol and the lower the residual
sugar the lower the density of our wines.

```{r echo=FALSE}
#code to plot alcohol to residual sugar to quality jitter plot
ggplot(aes(x = alcohol, y = residual.sugar, 
           color = quality), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```


```{r echo=FALSE}
#code to plot fixed acidity to volatile acidity to citric acid jitter plot
ggplot(aes(x = fixed.acidity, y = volatile.acidity, color = citric.acid), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

----
----

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the\
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

Mostly these were just a combination of bivariate conclusions less the fixed
acidity vs citric acid.

### Were there any interesting or surprising interactions between features?

I was surprised to find that in observing the relationships between all of our
acids, the fixed acidity was so closely related to the citric acid content.

# Final Plots and Summary

### Plot One: Residual Sugar

```{r echo=FALSE, message=FALSE, Plot_One}
#code to plot residual sugar bar graph
qplot(x = wine$residual.sugar, 
      main = "Residual Sugar",
      xlab = "Residual Sugar (g / L)", 
      ylab = "Count",
      binwidth = 1,
      color = I("#FFFFFF"),
      fill = I("#800020"),
      xlim = c(0, quantile(wine$residual.sugar, .99)))+
      scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
      scale_y_continuous(breaks = seq(0,1600,100))+
      coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))
```

### Description of Residual Sugar

This is a graph of the residual sugar in our wines in g/L (g/dm^3).
This graph shows us that the bulk of our data falls within 1.5 to 2.5 g/dm^3.
1030 of our wines or over 64% of our 1599 observations fall in this range, which 
is an unusually low amount of sugar in wines.

```{r echo=FALSE, }
#Equation to get the total # of wines that have residual sugar >= 1.5 and < 2.5
#This gets us roughly the value in that tall bar above.
total = 0

for (i in wine$residual.sugar) {
  if (i >= 1.5 & i < 2.5) {
    total  = total+ 1 
    }
  }
```


### Plot Two: Alcohol to Residual Sugar

```{r echo=FALSE, Plot_Two}
#code to plotresidual sugar to alcohol jitter plot
ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1, color = "red")+
  ggtitle("Alcohol to Residual Sugar")+
  ylab("Alcohol Content by Volume")+
  xlab("Residual Sugar (g/L)")+
  geom_smooth(method = "lm", formula = y~x, se = FALSE)+
  stat_cor()+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
  coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))
```

### Descriptionof Alcohol to Residual Sugar

In this graph we see the relationship between residual sugar in g/L and alcohol
content by volume. We see by the R coefficient that there is a very weak 
correlation between the two when we should expect a strong correlation. This
is likely due to our limited values of sugar where too many wines fall in a
very tight limit on our sugar scale. 

### Plot Three: Alcohol and Residual Sugar with Density

```{r echo=FALSE, Plot_Three}
#code to plot residual sugar to alcohol to density jitter plot
ggplot(aes(x = residual.sugar , y = alcohol, 
           color = density), data = wine) +
  ggtitle("Alcohol and Residual Sugar with Density")+
  ylab("Alcohol by Volume")+
  xlab("Residual Sugar g/dm^3")+
  geom_jitter(alpha = .5) +
  scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
  scale_color_gradient(high = 'green', low = 'red')+
  coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))+
  scale_y_continuous(breaks = seq(0,15,.5))
```

### Description of Alcohol and Residual Sugar with Density

This graph illustrates that despite the fact that our alochol and sugar ratios
are not what we expect them to be, one relationship that we did expect remains.
The red/orange area of the graph tends toward the top where it becomes more
of a green/orange on the bottom. This indicates the lower density is toward the
top where the alcohol content is higher and the higher density is toward the
bottom where the residual sugar is higher. 


# Reflection

I believe this dataset to be incomplete or not representative of a good variety
of wine due to the odd sugar content. Mostly I struggled with this concept as
I initially felt I had done something wrong when I discovered this in our data.
I was glad to find the explanation in the sugar content being so low. I was
also pleased with the relationship between the preservatives and the alcohol 
where it seemed the relationship between alcohol and the various preservatives
was vaguely negative which is what I expected. 

It would be interesting to see finer relationships between quality and ratios of
different substances, like the acid to sugar ratio and quality if the sugar was
easier to work with and the same with chloride to sugar and acid.

It was interesting to see that sulphates
were received more positively than most other aspects and that it is possible
to taste the total sulfur dioxide and that it's flavor made a noticeable impact
on quality. 
