---
output:
  html_document: default
  pdf_document: default
---
Red Wine Quality by Chelsey De Dios
========================================================
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
#importing libraries
library(gridExtra)
library(ggplot2)
library(tidyverse)
library(ggpubr)
```

```{r echo=FALSE, Load_the_Data}
#loading red wine data
wine <- read.csv("wineQualityReds.csv")
```

We will be exploring data regarding the qualities of nearly 1600 red wines.
This data set includes various objective observations on red wine and a rating of the wines based on analysis by a group of wine experts. I chose this data set as I used to be a server at a high-end restaurant and would be interested to know if the conventional knowledge taught to us to help customers is verifiable within this data set. 

# Univariate Plots Section

## Statistical Summary

```{r echo=FALSE, Univariate_Plots}
#summary of red wine data
summary(wine)
```
Here, in our statistical summary, we see we have mostly objective, measurable observations about the wine, with just quality being a subjective measure of the wines. There are 1599 observations and 13 variables.


## Data Structure

```{r echo=FALSE, message=FALSE, warning=FALSE}
#getting data structure
str(wine)
```
Now, looking at our data structure, we see we are dealing with some very small numbers. Quality, notably, is an integer. This casting is inconvenient for our purposes because it will cause the graphs to make singular plots. It would be better to cast the quality as numeric, so let's change that.

```{r echo=FALSE, message=FALSE, warning=FALSE}
#changing quality to a numeric value and observing the output
wine$quality <- as.numeric(wine$quality)
str(wine)
```


## Wine Quality

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot wine quality bar graph
qplot(x = wine$quality, 
      xlab = "Quality Rating 1-10", 
      binwidth = 1)+
      scale_x_continuous(breaks = seq(0,10,1))
```

It looks like most of the wine with of middling quality with most having a score of 5-6 out of 10. It would be interesting to learn about the background of the wines and wine experts to find why so few have an exceptionally poor or excellent rating.


## Alcohol Content By Volume

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol bar graph
qplot(x = wine$alcohol, 
      xlab = "Alcohol Content (% by volume)", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,15,.5))
```

Here we can see that the bulk of our alcohol content is between 9% and 11% by volume with a little bit of an outlier around ~14.75%


## Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot residual sugar bar graph
qplot(x = wine$residual.sugar, 
      xlab = "Residual Sugar (g / dm^3)", 
      binwidth = 1)+
      scale_x_continuous(breaks = seq(0,16,1))
```

The residual sugar is positively skewed, with most of the data within 1.5-3 g / dm^3. There are larger numbers, going up to around 15.5 g / dm^3. 

Seeing that most of the residual sugar is in the 1.5-3.5 g/dm^3 is significant. Sugar in wine varies greatly and can be anywhere from 0 to over 200 g/L (g/L is equivalent to g/dm^3). That we only have wines under 20 g/L says we are dealing with only dry wines. 

There should be a relationship between sugar and alcohol content, as wines with more alcohol should have less sugar. This relationship is because yeast consumes sugar to make alcohol in wine.

## Density

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot density bar graph
qplot(x = wine$density, 
      xlab = "density (g / cm^3)", 
      binwidth = .001)+
      scale_x_continuous(breaks = seq(0,2,.001 ))
```

Our density has a normal distribution with most wines falling between .995 and .999 g/cm^3. 

There should be a relationship between alcohol, sugar and density, as sugar rich wines should be thicker while alcohol rich wines should be thinner.


##  Sulphates

```{r echo=FALSE}
#code to plot sulphates bar graph
qplot(x = wine$sulphates, 
      xlab = "potassium sulphate (g / dm3)", 
      binwidth = .05)+
      scale_x_continuous(breaks = seq(0,2,.1 ))
```

Our sulfates seem to have a normal distribution save for a few outliers.

Sulfates are used to preserve wine, are antimicrobial and an antioxidant that leads to sulfur dioxide, or sulfites, in wine.

##  Total and Free Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot total sulfur dioxide bar graph
qplot(x = wine$total.sulfur.dioxide, 
      xlab = "total sulfur dioxide (mg / dm^3)", 
      binwidth = 10)+
      scale_x_continuous(breaks = seq(0,300,10 ))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to free sulfuree dioxide bar graph
qplot(x = wine$free.sulfur.dioxide, 
      xlab = "free sulfur dioxide (mg / dm^3)", 
      binwidth = 2)+
      scale_x_continuous(breaks = seq(0,72,2 ))
```

The free sulfur dioxide has a positive skew, as does the total sulfur dioxide. 
Winemakers may be trying to keep these numbers low as sulfites have an 
undeservedly bad reputation, a topic for another day. 

It would be interesting to see if the wine experts noticed any difference in sulfate/sulfite-rich wine and those less so. I expect that we will find that they didn't spot the difference. We should find that there is a relationship between sulfates/sulfites and alcohol content. Alcohol-rich wines should not need as much preservative as those wines with less alcohol.


## Fixed and Volatile Acidity

```{r echo=FALSE}
#code to plot fixed acidity bar graph
qplot(x = wine$fixed.acidity, 
      xlab = "fixed acidity", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,16,.5))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot volatile acidity bar graph
qplot(x = wine$volatile.acidity, 
      xlab = "Volatile Acidity", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,2,.1))
```

The volatile acidity also seems to have a nearly normal distribution. 

It will be interesting to see the relationship between sugar, chloride, acidity, citric acid, and quality later on.


## Citric Acid

```{r echo=FALSE}
#code to plot citric acid bar graph
qplot(x = wine$citric.acid, 
      xlab = "citric acid", 
      binwidth = .1)+
      scale_x_continuous(breaks = seq(0,1,.05))
```

Here we see that our citric acid is rather evenly distributed between 0 and .5.
It is interesting that the distribution fell this neatly.



# Univariate Analysis

### What is the structure of your dataset?

Our dataset has 1599 observations with 13 variables all numeric since we
converted our integer of quality to numeric to make the data easier to work with

We have many middling quality wines, making it more difficult to spot
what necessarily puts the higher quality wines at that rating. More meaningful conclusions could be drawn if the data had more observations of lower and higher quality wines.


### What is/are the main feature(s) of interest in your dataset?

* I am interested in what factors put some wines at a higher quality rating than others. I am particularly interested in whether sulfates/sulfites made much of a difference to our experts. 

* I am interested in the relationship of alcohol content to preservatives,
including acids and sulfates/sulfites.

* There should be a relationship between alcohol and sugar content and density. 

* I would like to explore the relationship between volatile acidity and citric
acid as I would expect that their volatile acidity would go up with the addition of citric acid.

### Of the features you investigated, were there any unusual distributions? \

Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I did change wine quality from integer to numeric so that it could be 
graphed on a continuous scale.

As far as unusual distributions, most of our data is either positively skewed or has a relatively normal distribution, suggesting that less is more for winemakers when it comes to any of these factors. Maybe they want to let the flavor of the grapes shine rather than having extreme of flavor in any direction.

The residual sugar of the wines is very low. We are dealing with a subset of very dry wines.
----
----

# Bivariate Plots Section

----

## Variables to Quality Comparisons

----

### Sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to sulphates jitter plot
ggplot(aes(x = quality, y = sulphates), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  xlab("quality")
```

It appears that sulfates in wine do not have a negative effect on quality, despite some people's misgivings about the nature of sulfates in food and beverage. 

In fact, according to this plot, it appears that the more sulfates were in the wine the higher the rating the wine received.


### Total Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to total sulfur dioxide jitter plot
ggplot(aes(x = quality, y = total.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  xlab("quality")
```

Here we see that the total sulfur dioxide seems to have a weak negative relationship with the quality. Indeed, our text file suggests that the more total sulfur dioxide there is, the more prominent the flavor, which must be unfavorable


### Free Sulfur Dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to  free sulfur dioxide jitter plot

ggplot(aes(x = quality, y = free.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  xlab("quality")
```

In the free sulfur dioxide and the total sulfur dioxide to quality graphs, we see a very weak relationship. There is likely no relationship between free sulfur dioxide content and the perceived quality of the wine.

### Fixed Acidity

```{r echo=FALSE}
#code to plot quality to fixed acidity jitter plot

ggplot(aes(x = quality, y = fixed.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

Our fixed acidity appears to have a weak positive relationship with the quality.


### Volatile Acidity

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to volatile acidity jitter plot

ggplot(aes(x = quality, y = volatile.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

More volatile acidity seems to decrease the quality with a borderline weak/moderate relationship.


### Citric Acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to citric acid jitter plot

ggplot(aes(x = quality, y = citric.acid), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The quality of wine seems to improve with citric acid with a weak relationship.


### Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to residual sugar jitter plot

ggplot(aes(x = quality, y = residual.sugar), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The residual sugar does not seem to have much of an effect on the quality. This relationship is likely since most of the wines have a very similar amount of residual sugar.


### Chlorides

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to chlorides jitter plot

ggplot(aes(x = quality, y = chlorides), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

There is a very weak negative correlation between salt/chlorides and quality.


### Density

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to density jitter plot

ggplot(aes(x = quality, y = density), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

A similarly weak relationship exists between density and quality, with a minor skew toward lower density/more watery wines. 

Lower density wines should have a higher alcohol content, and so it is hard to tell which of these variables cause the preference.

### pH

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to pH jitter plot

ggplot(aes(x = quality, y = pH), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

There does not seem to be much of a relationship between the quality and the pH.


### Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot quality to alcohol jitter plot

ggplot(aes(x = quality, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

The relationship between alcohol content and quality seems stronger than most of the data that we have looked at so far. It appears that the more alcohol, the higher the rating the wine received. 

Higher alcohol content leads to dryer flavors in wine, and this looks more and more like this tasting was intended to find the best dry wine.


## Residual Sugar to Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot residual sugar to alcohol jitter plot

ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(1,16,1))
```


This graph is notable because it does not point to the expected
conclusion, that the residual sugar amount would be inversely
proportionate to the amount of alcohol in the wine. 

Between 1.5g/dm^3 and 3 g/dm^3 of sugar, the alcohol content varies from less than 8.5% to over 14% by volume. 

We can see in the outlier range there is a negative relationship
with the alcohol content going down as the residual sugar goes up, but most of the data does not follow our expected trend. 

Our R-value seems to indicate a very weak positive correlation between our variables. This is likely due to the very limited range of sugar in our wines giving us unlikely data.

Let's zoom in on the bulk of the data area to see if we see any other trends.


```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot zoom in on residual sugar to alcohol jitter plot

ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(1.5,3,.1))+
  coord_cartesian(xlim = c(1.5,3))+
  geom_smooth(method = "lm", formula = y~x)
```

This graph does not at all show the expected relationship.


## Alcohol to Preservatives

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total sulfur dioxide jitter plot

ggplot(aes(x = alcohol, y = total.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to free sulfur dioxide jitter plot
ggplot(aes(x = alcohol, y = free.sulfur.dioxide), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to fixed acidity jitter plot
ggplot(aes(x = alcohol, y = fixed.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total volatile acidity jitter plot
ggplot(aes(x = alcohol, y = volatile.acidity), data = wine)+
  geom_jitter(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)
```

Here, as should be expected, we see that the higher the alcohol content, the lower the preservatives in the wine. 

The relationship is weak across the board, with volatile acidity and total sulfur dioxide having the strongest inverse relationships with alcohol.


## Volatile Acidity to Citric Acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot volatile acidity to citric acid scatter plot
ggplot(aes(x = volatile.acidity, y = citric.acid), data = wine)+
  geom_point(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  scale_y_continuous(breaks = seq(0, 1 , .1))+
  coord_cartesian(ylim = c(0,1))
```

There seems to be a moderate negative correlation between citric acid and volatile acidity. 

Since citric acid is added after the wine is made, I had expected that the volatile acidity would increase, creating a positive correlation.


## Density to Alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot density to alcohol jitter plot
ggplot(aes(x = density, y = alcohol), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,2,.001 ))+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

In this graph, the density of the wine goes down as the alcohol content goes up. 
Oddly, we would expect this because the alcohol is created by yeast eating sugar, so it is strange with the uniform sugar content that this relationship is maintained.


## Density to Residual Sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code to plot alcohol to total residual sugar jitter plot
ggplot(aes(x = density, y = residual.sugar), data = wine)+
  geom_jitter(alpha = .1)+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,2,.001 ))+
  geom_smooth(method = "lm", formula = y~x)+
  stat_cor()
```

Though the relationship is a bit weaker, we can see that the relationship between density and sugar is maintained where the wine should be denser the more sugar it contains.



# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset? Did you observe any interesting relationships between the other \
features (not the main feature(s) of interest)? What was the strongest \
relationship you found?


The most significant predictor of wine quality by itself was alcohol content. Alcohol content had a moderate relationship with wine quality, with an R-value of .48. 

Second to the alcohol content was the volatile acidity, where it seems that the more volatile acidity there was, the less desirable the wine. 
As explained in our text file, volatile acid leads to a vinegary taste in wine which many find offensive.

Citric acid seemed to be well-liked with a coefficient of .23. I remember a manager expressing that citric acid added a springy, light taste to the wine that people enjoyed, and it seems our experts agree to some extent. Our text file indicates something similar that the citric acid adds a 'freshness' to wine. 

There seemed to be no negative relationship with quality and sulfates in the alcohol, even perhaps, a weak positive correlation. The more total sulfur dioxide there was, the worse of a rating the wine got. The free sulfur dioxide seemed to make little difference in the wine quality.

The sugar to alcohol relationship should have been inverse, but according to this data, the correlation is weak. Despite this, the expected relationship of sugar to density and alcohol to density is as we expected, with the higher sugar wines being denser and the higher alcohol wines being less dense.

The strongest relationship was alcohol to density with a -.5 correlational coefficient indicating that there is a moderate relationship between those variables. 

Our total sulfur dioxide, free sulfur dioxide, fixed acidity, and volatile acidity to alcohol comparisons showed a weak negative relationship across the board, offering some credence to our hypotheses that the more alcohol the wine had, the fewer preservatives a wine make might add to it.




# Multivariate Plots Section

```{r echo=FALSE}
#code to plot fixed acidity to volatile acidity to citric acid jitter plot
ggplot(aes(x = fixed.acidity, y = volatile.acidity, color = citric.acid), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

This graph shows that while the citric acid decreases with volatile acidity, it increases with fixed acidity. I don't know why I didn't think to look at that before. It appears that it is just an acid that does not evaporate as readily as is necessary to be included in our volatile acidity. For fun, let's check out the bivariate graph of that relationship

```{r echo=FALSE}
#code to plot fixed acidity to citric acid scatter plot
ggplot(aes(x = fixed.acidity, y = citric.acid), data = wine)+
  geom_point(alpha = .1)+
  stat_cor()+
  geom_smooth(method = "lm", formula = y~x)+
  scale_y_continuous(breaks = seq(0, 1 , .1))+
  coord_cartesian(ylim = c(0,1))
```

Indeed there is a strong correlation between citric acid and fixed acidity

```{r echo=FALSE}
#code to plot alcohol to residual sugar to density jitter plot
ggplot(aes(x = alcohol, y = residual.sugar, 
           color = density), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

Here we show again that the lower the alcohol and the higher the residual sugar the higher the density, and the higher the alcohol, and the lower the residual sugar, the lower the density of our wines.

```{r echo=FALSE}
#code to plot alcohol to residual sugar to quality jitter plot
ggplot(aes(x = alcohol, y = residual.sugar, 
           color = quality), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```


```{r echo=FALSE}
#code to plot fixed acidity to volatile acidity to citric acid jitter plot
ggplot(aes(x = fixed.acidity, y = volatile.acidity, color = citric.acid), data = wine) +
  geom_jitter(alpha = .5) +
  scale_color_gradient(high = 'green', low = 'red')
```

----
----

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the\
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

For the most part, these were just a combination of bivariate conclusions less the fixed acidity vs citric acid.

### Were there any interesting or surprising interactions between features?

I was surprised to find that, in observing the relationships between all of our acids, the fixed acidity was so closely related to the citric acid content.

# Final Plots and Summary

### Plot One: Residual Sugar

```{r echo=FALSE, message=FALSE, Plot_One}
#code to plot residual sugar bar graph
qplot(x = wine$residual.sugar, 
      main = "Residual Sugar",
      xlab = "Residual Sugar (g / L)", 
      ylab = "Count",
      binwidth = 1,
      color = I("#FFFFFF"),
      fill = I("#800020"),
      xlim = c(0, quantile(wine$residual.sugar, .99)))+
      scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
      scale_y_continuous(breaks = seq(0,1600,100))+
      coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))
```

### Description of Residual Sugar

This is a graph of the residual sugar in our wines in g/L (g/dm^3).
This graph shows us that the bulk of our data falls within 1.5 to 2.5 g/dm^3. 1030 of our wines or over 64% of our 1599 observations fall in this range; an unusually low amount of sugar in wines.

```{r echo=FALSE, }
#Equation to get the total # of wines that have residual sugar >= 1.5 and < 2.5
#This gets us roughly the value in that tall bar above.
total = 0

for (i in wine$residual.sugar) {
  if (i >= 1.5 & i < 2.5) {
    total  = total+ 1 
    }
  }
```


### Plot Two: Alcohol to Residual Sugar

```{r echo=FALSE, Plot_Two}
#code to plotresidual sugar to alcohol jitter plot
ggplot(aes(x = residual.sugar, y = alcohol), data = wine)+
  geom_jitter(alpha = .1, color = "red")+
  ggtitle("Alcohol to Residual Sugar")+
  ylab("Alcohol Content by Volume")+
  xlab("Residual Sugar (g/L)")+
  geom_smooth(method = "lm", formula = y~x, se = FALSE)+
  stat_cor()+
  scale_y_continuous(breaks = seq(0,15,.5))+
  scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
  coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))
```

### Descriptionof Alcohol to Residual Sugar

In this graph, we see the relationship between residual sugar in g/L and alcohol content by volume. We see by the R coefficient a very weak correlation between the two when we expect a stronger correlation. This is likely due to our limited values of sugar where too many wines fall in a very tight limit on our sugar scale. 

### Plot Three: Alcohol and Residual Sugar with Density

```{r echo=FALSE, Plot_Three}
#code to plot residual sugar to alcohol to density jitter plot
ggplot(aes(x = residual.sugar , y = alcohol, 
           color = density), data = wine) +
  ggtitle("Alcohol and Residual Sugar with Density")+
  ylab("Alcohol by Volume")+
  xlab("Residual Sugar g/dm^3")+
  geom_jitter(alpha = .5) +
  scale_x_continuous(breaks = seq(0,quantile(wine$residual.sugar, .99),.5))+
  scale_color_gradient(high = 'green', low = 'red')+
  coord_cartesian(xlim = c(0,quantile(wine$residual.sugar, .99)))+
  scale_y_continuous(breaks = seq(0,15,.5))
```

### Description of Alcohol and Residual Sugar with Density

This graph illustrates that despite the alcohol and sugar ratios not being what we expected, one relationship that we did remains. 

The red/orange area of the graph tends toward the top, where it becomes more of a green/orange on the bottom. 

This indicates the lower density is toward the top, where the alcohol content is higher, and the higher density is toward the bottom, where the residual sugar is higher. 


# Reflection

I believe this dataset to be incomplete or not representative of a good variety
of wine due to the odd sugar content. Mostly I struggled with this concept as
I initially felt I had done something wrong when I discovered this in our data.
I was glad to find the explanation in the sugar content being so low. I was
also pleased with the relationship between the preservatives and the alcohol 
where it seemed the relationship between alcohol and the various preservatives
was vaguely negative which is what I expected. 

It would be interesting to see finer relationships between quality and ratios of
different substances, like the acid to sugar ratio and quality if the sugar was
easier to work with and the same with chloride to sugar and acid.

It was interesting to see that sulphates
were received more positively than most other aspects and that it is possible to taste the total sulfur dioxide and that it's flavor made a noticeable impact on quality. 
